TrueSkill Through Time: the \proglang{Python} Package

### 2020-07-20 article.tex
Paper TTT: Agregando ejemplos
Paper TTT: esquema de los ejemplos con dataset

\usepackage{bm} % \bm{\alpha} bold greek symbol
\usepackage[makeroom]{cancel} % \cancel{} \bcancel{} etc
\usepackage{wrapfig} % \begin{wrapfigure} Pone figura al lado del texto
\usepackage{mdframed}
\usepackage{algorithm}
%\usepackage{quoting}
\usepackage{mathtools}	
\usepackage{tikz}

@@

\begin{leftbar}
For code input and output, the style files provide dedicated environments.
Either the ``agnostic'' \verb|{CodeInput}| and \verb|{CodeOutput}| can be used
or, equivalently, the environments \verb|{Sinput}| and \verb|{Soutput}| as
produced by \fct{Sweave} or \pkg{knitr} when using the \code{render_sweave()}
hook. Please make sure that all code is properly spaced, e.g., using
\code{y = a + b * x} and \emph{not} \code{y=a+b*x}. Moreover, code input should
use ``the usual'' command prompt in the respective software system. For
\proglang{R} code, the prompt \code{"R> "} should be used with \code{"+  "} as
the continuation prompt. Generally, comments within the code chunks should be
avoided -- and made in the regular {\LaTeX} text instead. Finally, empty lines
before and after code input/output should be avoided (see above).
\end{leftbar}

\begin{figure}[t!]
\centering
\includegraphics{jsslogo}
\caption{\label{fig:quine} Frequency distribution for number of days absent
from school.}
\end{figure}

>>>>

\usepackage{bm} % \bm{\alpha} bold greek symbol
\usepackage[makeroom]{cancel} % \cancel{} \bcancel{} etc
\usepackage{wrapfig} % \begin{wrapfigure} Pone figura al lado del texto
\usepackage{mdframed}
\usepackage{algorithm}
%\usepackage{quoting}
\usepackage{mathtools}	
\usepackage{tikz}
\usepackage{csvsimple}
\usepackage{listings}
\usepackage{hyperref}
\definecolor{dkgreen}{rgb}{0,0.6,0}
\definecolor{mauve}{rgb}{0.58,0,0.82}

@@

\begin{leftbar}
For code input and output, the style files provide dedicated environments.
Either the ``agnostic'' \verb|{CodeInput}| and \verb|{CodeOutput}| can be used
or, equivalently, the environments \verb|{Sinput}| and \verb|{Soutput}| as
produced by \fct{Sweave} or \pkg{knitr} when using the \code{render_sweave()}
hook. Please make sure that all code is properly spaced, e.g., using
\code{y = a + b * x} and \emph{not} \code{y=a+b*x}. Moreover, code input should
use ``the usual'' command prompt in the respective software system. For
\proglang{R} code, the prompt \code{"R> "} should be used with \code{"+  "} as
the continuation prompt. Generally, comments within the code chunks should be
avoided -- and made in the regular {\LaTeX} text instead. Finally, empty lines
before and after code input/output should be avoided (see above).
\end{leftbar}
This tutorial will guide you through some of typicals \textbf{TTT} package application.
Familiarity with Python is assumed, so if you are new to Pythom there is plenty of online documentation like the official Python documentation
page at \href{http://www.python.org/doc/}{\textcolor{blue}{http://www.python.org/doc/}}.
In addition to the module \textbf{TTT}, the libraries collections, dateutil and mathematics(Gaussian) are also required.
In this section its show some applications, starting with an example of Trueskill of 1vs1, then an example with a data set, and the last one a first example of Trueskill Through Time.

\subsection{Example 1: Trueskill 1vs1}
The first examples is the most basic one we figure out. Its one of the first examples in the official python package of Trueskill. Ower library, its almost four times faster than the official.

\lstinputlisting{./code/Example1.py}

\subsection{Example 2: Trueskill dataset}
For this example  we want to show hoy trueskill can be used with a data set. For this we will use de as input Table \ref{tab:csvExample2}. Its importan to de Result intput as shown. In this case we will use the libraty Pandas, but it can be done with out it, the only important its how to upload the data set and loop with it.

\begin{table}[h!]
	\centering
	%\resizebox{\textwidth}{!}{%
		\begin{tabular}{llll}
			\hline
			Id  & Player1        & Player2        & Result \\ \hline
			101 & 'matt64'       & 'Chuk'         & [1,0]      \\
			102 & 'matt64'       & 'David'        & [1,0]      \\
			103 & 'ggg'          & 'matt64'       & [0,1]      \\
			104 & 'Chuk'         & 'David'        & [0,1]      \\
			105 & 'ggg'          & 'TheProffesor' & [0,1]      \\
			106 & 'ggg'          & 'matt64'       & [1,0]      \\
			107 & 'Chuk'         & 'TheProffesor' & [0,1]      \\
			108 & 'Chuk'         & 'NaT'          & [1,0]      \\
			109 & 'David'        & 'TheProffesor' & [1,0]      \\
			110 & 'David'        & 'Chuk'         & [1,0]      \\
			111 & 'TheProffesor' & 'Chuk'         & [0,1]      \\
			112 & 'Mona'         & 'matt64'       & [1,0]      \\
			113 & 'TiNi'         & 'David'        & [1,0]      \\
			113 & 'Chuk'         & 'matt64'       & [1,0]      \\
			115 & 'ggg'          & 'matt64'       & [1,0]      \\ \hline
		\end{tabular}%
	%}
	\caption{An example of Data set, used in example 2. }
	\label{tab:csvExample2}
\end{table}

\lstinputlisting{./code/Example2.py}
\subsection{Example 3: Trueskill True Time}
One of the advantage of \textbf{TTT}, its the way that the algorithm pass information to de past to the future and vice versa, getting a more accurate estimation. In adition, it can define a temporal batch were its supose that in there the order of the games it doesn't matter. For that, we use the next example. Three player, three games, that each one wins one game and lose the other one. So if we do trueskill, the order of how we compute the games will have importance, making at the end three player with three different skill. With \textbf{TTT} this kind of problem its solve.

\lstinputlisting{./code/Example3.py}

\begin{figure}[h!]
\centering
\includegraphics{jsslogo}
\caption{\label{fig:quine} Frequency distribution for number of days absent
from school.}
\end{figure}
